quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-07-06 paper-quollr.Rmd
Add figure title for Figure 5

```{r algo-steps, eval=knitr::is_latex_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}
scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

```{r, eval=knitr::is_latex_output()}
scurve_proj_umap_model1 + scurve_proj_umap_model2 + scurve_proj_umap_model3 + scurve_proj_umap_model4 + 
  plot_layout(ncol = 4)
```

>>>>

```{r algo-steps, eval=knitr::is_latex_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}

scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.pos='H', fig.cap="`langevitour` output of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

show_langevitour(
  point_data = df_exe, 
  edge_data = trimesh
  )
```

```{r, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="$2\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

scurve_proj_umap_model1 + scurve_proj_umap_model2 + 
  scurve_proj_umap_model3 + scurve_proj_umap_model4 + 
  plot_layout(ncol = 4)
```

### 2025-07-06 paper-quollr.tex
Add figure title for Figure 5

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1} \caption{$2 ext{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model.}\label{fig:unnamed-chunk-27}
\end{figure}
